Results Coding

### 2023-12-07 analysis/practiceCoding_AW.Rmd
Code update
Also, corrected readme file for prominent article sample instructions

#table_length <- table(PPC_length$ppc_length, PPC_length$ppc_name)
table(dj_prominent$ppc_length, dj_prominent$ppc_name)
table(dj_random$ppc_length, dj_random$ppc_name)
```

@@

@@

dj_prominent %>%
  filter(!is.na(ppc_length)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ "Quantitative",
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_length)
  )) %>%
  ggplot(mapping = aes(x = ppc_length, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5) +
  theme_bw() +
  coord_flip() +
  scale_y_continuous(limits = c(0, 41)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.5)) +
  labs(x = "Length Limit Statement", y = "Count", fill = "PPC Type")

@@

>>>>

#table_length <- table(PPC_length$ppc_length, PPC_length$ppc_name)
table(dj_prominent$ppc_length, dj_prominent$ppc_name)
table(dj_random$ppc_length, dj_random$ppc_name)
```
```{r}

d_journals %>%  
  filter(sample_id == "prominent" | sample_id == "both") %>%
  filter(ppc_type == "A") %>%
  filter(!is.na(has_ppc)) %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'Archive',
    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
      has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
    has_ppc == 'YES' ~ 'Yes',
    TRUE ~ has_ppc
    )) %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ggplot(aes(x = "has_ppc", y = count, fill = has_ppc)) +
  geom_bar(stat = "identity") +
  theme_bw() +
  scale_fill_brewer(palette = "Oranges") +
  labs(title = "Prominent Journal PPC Acceptance", x = "Accepts PPC", y = "Percentage", fill = "PPC Policy")

```
```{r}
library(dplyr)
library(ggplot2)

# Filter and process data for ppc_length
ppc_length_data <- d_journals %>%
  filter(sample_id %in% c("prominent", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_length) %>%
  summarise(count = n())

# Filter and process data for ppc_time
ppc_time_data <- d_journals %>%
  filter(sample_id %in% c("prominent", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_time) %>%
  summarise(count = n())

# Combine the data and unite the columns
combined_data <- bind_rows(
  ppc_length_data %>% mutate(Code = "Length"),
  ppc_time_data %>% mutate(Code = "Time-to-submit")
) %>%
unite(limits, ppc_length, ppc_time) %>%
  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
                   limits == "Qualitative_NA" ~ "Qualitative",
                   limits == "Quantitative_NA" ~ "Quantitative",
                   limits == "NA_Not Stated" ~ "Not Stated",
                   limits == "NA_Qualitative" ~ "Qualitative",
                   limits == "NA_Quantitative" ~ "Quantitative",
                   TRUE ~ as.character(limits)
                   ))

# Create a stacked bar chart
ggplot(combined_data, aes(x = Code, y = count, fill = limits)) +
  geom_bar(stat = "identity", 
           position = "stack",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs( x = "Restriction Type", y = "Count", fill = "Restriction")

```
# COMBINED GRAPHS OF PPC POLICY AND RESTRICTIONS (PROMINENT)
```{r}

# Create the first graph
graph1 <- ggplot(combined_data, aes(x = Code, y = count, fill = limits)) +
  geom_bar(stat = "identity", 
           position = "stack",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(x = "Restriction Type", y = "Count", fill = "Restrictions")

# Create the second graph
graph2 <- d_journals %>%
  filter(sample_id == "prominent" | sample_id == "both") %>%
  filter(ppc_type == "A") %>%
  filter(!is.na(has_ppc)) %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'Archive',
    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
    has_ppc == 'YES' ~ 'Yes',
    TRUE ~ has_ppc
  )) %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ggplot(aes(x = "", y = count, fill = has_ppc)) +
  geom_bar(stat = "identity",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Oranges") +
  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")

# Arrange both graphs in the same figure
combined_plots <- graph2 + graph1
combined_plots

ggsave(filename = "Prominent_statements.png", plot = last_plot(), device = "png")
```
# COMBINED GRAPHS OF PPC POLICY AND RESTRICTIONS (RANDOM)
```{r}

# Filter and process data for ppc_length
ppc_length_random <- d_journals %>%
  filter(sample_id %in% c("random", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_length) %>%
  summarise(count = n())

# Filter and process data for ppc_time
ppc_time_random<- d_journals %>%
  filter(sample_id %in% c("random", "both")) %>%
  filter(!is.na(ppc_name)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_time = case_when(
    ppc_time %in% c(13.05, 26.1, 39.15, 4, 52) ~ 'Quantitative',
    ppc_time == "NOT STATED" ~ "Not Stated",
    TRUE ~ 'Qualitative'
  )) %>%
  group_by(ppc_time) %>%
  summarise(count = n())

# Combine the data and unite the columns
combined_data_random <- bind_rows(
  ppc_length_random %>% mutate(Code = "Length"),
  ppc_time_random %>% mutate(Code = "Time-to-submit")
) %>%
unite(limits, ppc_length, ppc_time) %>%
  mutate(limits = case_when(limits == "Not Stated_NA" ~ "Not Stated",
                   limits == "Qualitative_NA" ~ "Qualitative",
                   limits == "Quantitative_NA" ~ "Quantitative",
                   limits == "NA_Not Stated" ~ "Not Stated",
                   limits == "NA_Qualitative" ~ "Qualitative",
                   limits == "NA_Quantitative" ~ "Quantitative",
                   TRUE ~ as.character(limits)
                   ))

# Create the first graph
graph4 <- ggplot(combined_data_random, aes(x = Code, y = count, fill = limits)) +
  geom_bar(stat = "identity", 
           position = "stack",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Blues") +
  labs(x = "Restriction Type", y = "Count", fill = "Restrictions")

# Create the second graph
graph3 <- d_journals %>%
  filter(sample_id == "random" | sample_id == "both") %>%
  filter(ppc_type == "A") %>%
  filter(!is.na(has_ppc)) %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'Archive',
    has_ppc == 'NO EXPLICIT' ~ 'No Explicit',
    has_ppc == 'NO IMPLICIT' ~ 'No Implicit',
    has_ppc == 'YES' ~ 'Yes',
    TRUE ~ has_ppc
  )) %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ggplot(aes(x = "", y = count, fill = has_ppc)) +
  geom_bar(stat = "identity",
           colour = "black") +
  theme_bw() +
  scale_fill_brewer(palette = "Oranges") +
  labs(x = "Journal Policy", y = "Count", fill = "Accepts PPC")

# Arrange both graphs in the same figure
combined_plots <- graph3 + graph4
combined_plots

ggsave(filename = "Random_statements.png", plot = last_plot(), device = "png")

```{r}
library(dplyr)
library(ggplot2)

d_journals %>%
  filter(sample_id %in% c("prominent", "both")) %>%
  filter(ppc_type == "A") %>%
  filter(!is.na(has_ppc) & !is.na(ppc_length)) %>%
  mutate(has_ppc = case_when(
    has_ppc == 'ARCHIVE' ~ 'Archive',
    has_ppc %in% c('NO EXPLICIT', 'NO IMPLICIT') ~ 'No',
    has_ppc == 'Yes' ~ 'Yes',
    TRUE ~ as.character(has_ppc)
  )) %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1100, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ 'Quantitative',
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_length)
  )) %>%
  group_by(category = c("has_ppc", "ppc_length"), variable = case_when(
    category == "has_ppc" ~ has_ppc,
    category == "ppc_length" ~ ppc_length
  )) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ggplot(aes(x = category, y = percentage, fill = variable)) +
  geom_bar(stat = "identity") +
  facet_wrap(~category, scales = "free") +
  theme_bw() +
  scale_fill_brewer(palette = "Oranges") +
  labs(title = "Prominent Journal PPC Acceptance", x = "Accepts PPC", y = "Percentage", fill = "Variable")

@@

#TEST CHATGPT
```{r}

# Reshape the data to long format
my_tibble_long <- dj_prominent %>%
  gather(variable, category, has_ppc, ppc_length, ppc_time)

# Create the bar graph
my_tibble_long %>%
  filter(!is.na(ppc_length)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ "Quantitative",
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_length)
  )) %>%
ggplot(aes(x = category, fill = variable)) +
  geom_bar(position = "dodge") +
  labs(x = "Categories", y = "Count") +
  theme_minimal()

@@

dj_prominent %>%
  filter(!is.na(ppc_length)) %>%
  filter(has_ppc != "ARCHIVE") %>%
  mutate(ppc_length = case_when(
    ppc_length %in% c(1000, 1200, 1500, 2000, 2500, 2650, 3000, 3500, 400, 500, 5000, 750, 800, 8000) ~ "Quantitative",
    ppc_length == "NOT STATED" ~ "Not Stated",
    TRUE ~ as.character(ppc_length)
  )) %>%
  ggplot(mapping = aes(x = ppc_length, fill = ppc_name)) +
  geom_bar(position = "stack",
           colour = "black",
           width = 0.5) +
  theme_bw() +
  scale_y_continuous(limits = c(0, 41)) +
  scale_fill_brewer(palette = "Blues") +
  theme(legend.position = c(0.9, 0.5)) +
  labs(x = "Length Limit Statement", y = "Count", fill = "PPC Type")

@@

```
 #Coder Disagreements
```{r}

d_journals %>%
  filter(coder_id != "FINAL (TEH)") %>%
